Discussion

### 2023-03-16 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.Rmd
abstract

    affiliation   : "1", "2"

@@

 We present a paradigm that is suitable for determining individual SVs of ER strategies. 
 Using a multilevel modelling approach, it will be investigated whether individual SVs can be explained by effectiveness (subjective arousal, facial muscle activity) and subjective effort. 
 Relations of SVs to personality traits will be explored.
keywords          : "emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis"
wordcount         : "XXXXX"

>>>>

    affiliation   : "1,2"

@@

 We present a new paradigm for quantifying individual SVs of ER strategies by offering monetary values for ER strategies in an iterative process. 
 $N=120$ participants first conducted an ER paradigm with the strategies distraction, distancing, and suppression.
 Afterwards, individual SVs were determined using the new CAD paradigm.
 SVs significantly predicted later choice for an ER strategy ($\chi^2(4, \textit{n} = 119)=115.40$, $p<.001$, $BF10=1.62*1021$).
 Further, SVs were associated with Corrugator activity ($t(5, 618.96)=2.09$, $p=.037$, $f^2<0.001$), subjective effort ($t(5, 618.96)=-13.98$, $p<.001$, $f^2=0.035$), and self-reported utility ($t(5, 618.96)=29.49$, $p<.001$, $f^2=0.155$).
 SVs were further associated with self-control ($t(97.97)=2.04$, $p=.044$, $f^2=0.002$), but not with flexible ER. 
 With our paradigm, we were able to determine subjective values. 
 The trait character of the values will be discussed.
keywords          : "emotion regulation, regulatory effort, effort discounting, registered report, emotion regulation choice, emotion regulation flexibility, electromyography"
wordcount         : "about 9000"
